### 2019-12-17 paper/educ_work_over_time.tex
Begin discussion of falling female labor force participation

Despite the increasing level of female education the female labor force participation has
decreased over time.

>>>>

Even as the level of female education has increased the female labor force participation 
has decreased over time [should this be by level of education?].

[Discuss recent papers on labor supply in India]

To place my results in context, Figure XX shows the percent of married women who are 
working at the time of the survey by age group.%
\footnote{
This question is the only question on labor force participation consistently available 
across all four surveys.
Since the question is asked only of married women it is possible that the overall
female labor force participation might have developed differently, especially since
many young, unmarried women have begun working in, for example, the business process 
outsourcing industry [TK cite Jensen 2012 QJE].
}

The declines over the the four rounds of the NFHS are in line with what previous
research has found using other data sets [TK cite Bhargava 2018 and 2019, Chatterjee 2018].
Finding a decline in labor force participation in the beginning of development is
in line with the hypothesis of a U-shaped labor force participation as a country
develop [TK cite Goldin 1994, Chatterjee 2018].

The theories on the relationship between education and birth spacing often works 
through the changes in the opportunity cost of time. 
If women are unlikely to work, this makes the predictions that are based on
opportunity cost less relevant. 
instead, theories that emphasize income effects or effects of spacing become
more relevant.
